Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-08-12 BioinformaticsRevison/bioinformaticspaper.tex
getting close to final revisions

We repeated the single-locus analyses as first performed \citep{nicod2016genome} but some exceptions. We 
focused on autosomal SNPs, our analyses were based on SNP genotypes  rather than SNP dosages, 
we sought to control the false positive rate not false discovery rate of the methods, and significance thresholds were 
found empirically via permutation \citep{doerge1996permutation}.

@@

\section{Discussion/Conclusion}
Eagle is a new linear mixed model based method (and R package) for multi-locus association mapping. It advances the state of association mapping in several ways. 
First, its computational footprint is much smaller than other multi-locus implementations. Eagle makes multi-locus analysis 
practical, even when the datasets are large. Second, the results from
 Eagle are immediately interpretable. They are the set of SNPs in strongest association with the trait where 
each SNP identifies a separate genomic region of interest. Third, it treats association mapping as a model selection problem, avoiding 
 multiple testing issues. 
 As we saw in the simulation study, Eagle has considerably higher power than single-locus methods but is comparable in run time.
Also, when analysing the mouse data, Eagle found more than double the SNP-trait associations than 
with single-locus association mapping, the method of choice. \textcolor{red}{Furthermore, because we converted the SNP dosages of the 
original study into genotypes and focused our analyses on these data, the validity of the extra findings were able to  be confirmed 
against the original findings}. These extra findings were all found to be true.

>>>>

We repeated the single-locus analyses as first performed \citep{nicod2016genome} but some exceptions. We 
focused on autosomal SNPs, our analyses were based on SNP genotypes  rather than SNP dosages, 
we sought to control the false positive rate not false discovery rate of the methods, and significance thresholds were 
found empirically via permutation \textcolor{red}{\citep{doerge1996permutation}}.

@@

\section{Discussion/Conclusion}
Eagle is a new linear mixed model based method (and R package) for multi-locus association mapping. It advances the state of association mapping in several ways. 
First, its computational footprint is much smaller than other multi-locus implementations. Eagle makes multi-locus analysis 
practical, even when the datasets are large. Second, the results from
 Eagle are immediately interpretable. They are the set of SNPs in strongest association with the trait where 
each SNP identifies a separate genomic region of interest. Third, it treats association mapping as a model selection problem, avoiding 
 multiple testing issues. 
 As we saw in the simulation study, Eagle has considerably higher power than single-locus methods but is comparable in run time.
Also, when analysing the mouse data, Eagle found more than 50\% the SNP-trait associations than 
with single-locus association mapping, the method of choice. \textcolor{red}{Furthermore, because we converted the SNP dosages of the 
original study into genotypes and focused our analyses on these data, the validity of the extra findings were able to  be confirmed 
against the original findings}. These extra findings were all found to be true.
